\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-08-31 analysis/paper/paper.tex
final edits for CS4

Survival analysis and the comparison of event rates has been greatly
influenced over the last 50 years by the partial likelihood approach of
the Cox proportional hazard model \citep{cox1972regression}. This
approach provides a flexible way of assessing the influence of
covariates on the hazard function, without the need to specify a
parametric survival model. This flexibility comes at the cost of
decoupling the baseline hazard from the effect of the covariates. To
recover the whole survival curve---or the cumulative incidence function
(CIF)---we then need to separately estimate the baseline hazard
\citep{breslow1972discussion}. This in turn leads to stepwise estimates
of the survival function.

@@

With the goal of fitting smooth-in-time hazard functions, Hanley \&
Miettinen \citeyearpar{hanley2009fitting} proposed a general framework
for estimating fully parametric hazard models via logistic regression.
Their approach provides users that are familiar with generalized linear
models with a natural way of fitting parametric survival models.
Moreover, their framework is very flexible: general functions of time
can be estimated (e.g.~using splines or general additive models), and
hence these models retain some of the flexibility of Cox's partial
likelihood approach.

@@

\caption{\label{tab:bmtcrr-cis}Estimates and confidence intervals for the hazard ratios for each coefficient. Both estimates from case-base sampling and Cox regression are presented.}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Case-Base} & \multicolumn{2}{c}{Cox} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Covariates & HR & 95\% CI & HR & 95\% CI\\
\midrule
Sex & 0.70 & (0.4, 1.23) & 0.68 & (0.39, 1.19)\\
Disease & 0.53 & (0.29, 0.95) & 0.52 & (0.29, 0.93)\\
Phase (CR2 vs. CR1) & 1.12 & (0.45, 2.78) & 1.21 & (0.48, 3.02)\\
Phase (CR3 vs. CR1) & 1.45 & (0.37, 5.66) & 1.67 & (0.43, 6.5)\\
Phase (Relapse vs. CR1) & 4.04 & (1.88, 8.68) & 4.55 & (2.09, 9.9)\\
\addlinespace
Source & 1.48 & (0.48, 4.54) & 1.46 & (0.47, 4.54)\\
Age & 0.99 & (0.97, 1.01) & 0.99 & (0.97, 1.02)\\
\bottomrule
\end{tabular}
\end{table}

@@

Figure \ref{fig:compAbsrisk} shows the absolute risk curves for both
case-base sampling and the Fine-Gray model. As we can see, the two
approaches agree quite well for AML; however, there seems to be a
difference of about 5\% between the two curves for ALL. This difference
does not appear to be significant: the curve from case-base sampling is
contained within a 95\% confidence band around the Fine-Gray absolute
risk curve (figure not shown). \# Case study 3---SUPPORT Data

@@

Next, we can use the object \code{cbFull} to estimate the absolute risk
curve on the test data. We first create a matrix \code{newx} containing
the relevant variables. Using \code{times}, we specify the time points
at which the cumulative incidence will be computed. Finally, using the
parameter \code{s = "lambda.1se"}, we specify at which value of the
tuning parameter we want to retrieve the coefficient estimates.

@@

@@

\caption{\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used to generate the curves. The Cox-based curves appear to be smooth, but this is due to the 1703 follow-up times seen while fitting the models and the 319 time points used to estimate the curves. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest Brier scores over follow-up time.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3FinalBrier} (A). There is separation between the
curves, but it is minimal. To better demonstrate the differences in
performance between the models, we compare Brier scores over time. In
Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our
penalized logistic regression model compared to both Cox regression
models. The differences, however, are minimal. All three outperform the
Kaplan-Meier model.

@@

In the previous case studies, we only considered covariates that were
fixed at baseline. In this next case study, we will use the Stanford
Heart Transplant data
\citep[\citet{crowley1977covariance}]{clark1971cardiac} to show how
case-base sampling can also be used in the context of time-varying
covariates. As an example that already appeared in the literature,
case-base sampling was used to study vaccination safety, where the
exposure period was defined as the week following vaccination
\citep{saarela2015case}. Hence, the main covariate of interest,
i.e.~exposure to the vaccine, was changing over time. In this context,
case-base sampling offers an efficient alternative to nested
case-control designs or self-matching.

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 
#>    827    790    788
\end{CodeOutput}
\end{CodeChunk}

As we can see, the best fit is the third model. By visualizing the
hazard functions for both exposed and unexposed individuals, we can more
clearly see how the hazards are no longer proportional.

@@

@@

@@

As a methodological framework, case-base sampling is very flexible. This
flexibility has been explored before in the literature: for example,
Saarela and Hanley \citeyearpar{saarela2015case} used case-base sampling
to model a time-dependent exposure variable in a vaccine safety study.
As another example, Saarela and Arjas \citeyearpar{saarela2015non}
combined case-base sampling and a Bayesian non-parametric framework to
compute individualized risk assessments for chronic diseases. In the
case studies above, we further explored this flexibility along two
fronts. On the one hand, we showed how splines could be used as part of
the linear predictor to model the effect of time on the hazard. This
strategy yielded estimates of the survival function that were
qualitatively similar to semiparametric estimates derived from Cox
regression; however, case-base sampling led to estimates of the survival
function that \emph{vary smoothly in time} and are thus easier to
interpret. On the other hand, we also displayed the flexibility of
case-base sampling by showing how it could be combined with penalized
logistic regression to perform variable selection. Even though we did
not illustrate it in this article, case-base sampling can also be
combined with the framework of \emph{generalized additive models}. This
functionality has already been implemented in the package. Similarly,
case-base sampling can be combined with quasi-likelihood estimation to
fit survival models that can account for the presence of
over-dispersion. All of these examples illustrate how the case-base
sampling framework in general, and the package \pkg{casebase} in
particular, allows the user to fit a broad and flexible family of
survival functions.

@@

This report was generated on 2020-08-25 12:59:22 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
#> LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.6             glue_1.4.1               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.1              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.1               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.06.25 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.0.1     fs_1.4.2           
#>  [7] base64enc_0.1-3     rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.0      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.61       tools_4.0.2         gtable_0.3.0       
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        conquer_1.0.1       iterators_1.0.12   
#> [37] xfun_0.16           rvest_0.3.6         lifecycle_0.2.0    
#> [40] polspline_1.1.19    muhaz_1.2.6.1       MASS_7.3-51.6      
#> [43] zoo_1.8-8           hms_0.5.3           sandwich_2.5-1     
#> [46] SparseM_1.78        RColorBrewer_1.1-2  rticles_0.14       
#> [49] yaml_2.2.1          gridExtra_2.3       rms_6.0-1          
#> [52] rpart_4.1-15        latticeExtra_0.6-29 stringi_1.4.6      
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.7         
#> [58] shape_1.4.4         mets_1.2.7.1        rlang_0.4.7        
#> [61] pkgconfig_2.0.3     matrixStats_0.56.0  evaluate_0.14      
#> [64] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [67] cmprsk_2.2-10       tidyselect_1.1.0    deSolve_1.28       
#> [70] R6_2.4.1            generics_0.0.2      Hmisc_4.4-0        
#> [73] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [76] pillar_1.4.6        haven_2.3.1         foreign_0.8-80     
#> [79] mgcv_1.8-31         nnet_7.3-14         mstate_0.2.12      
#> [82] modelr_0.1.8        crayon_1.3.4        rmarkdown_2.3      
#> [85] jpeg_0.1-8.1        grid_4.0.2          readxl_1.3.1       
#> [88] blob_1.2.1          reprex_0.3.0        digest_0.6.25      
#> [91] webshot_0.5.2       numDeriv_2016.8-1.1 stats4_4.0.2       
#> [94] munsell_0.5.0       viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    master /home/jesseislam/Documents/gits/cbpaper
#> Remote:   master @ origin (git@github.com:Jesse-Islam/cbpaper.git)
#> Head:     [ffe8b03] 2020-08-25: Merge branch 'master' into sbmaster
\end{CodeOutput}
\end{CodeChunk}

>>>>

Survival analysis and the comparison of event rates has been greatly
influenced over the last 50 years by the partial likelihood approach of
the Cox proportional hazard model \citep{cox1972regression}. This
approach provides a flexible way of assessing the influence of
covariates on the hazard function, without the need to specify a
parametric survival model. This flexibility comes at the cost of
decoupling the baseline hazard from the effect of the covariates. To
recover the whole survival curve---or the cumulative incidence function
(CIF)---we then need to separately estimate the baseline hazard
\citep{breslow1972discussion}. This in turn leads to stepwise estimates
of the survival function that can be hard to interpret.

@@

With the goal of fitting smooth-in-time hazard functions, Hanley \&
Miettinen \citeyearpar{hanley2009fitting} proposed a general framework
for estimating fully parametric hazard models via logistic regression.
Their main idea is simple: comparing person-moments when the event of
interest occurred with moments when patients were at risk. Their
approach provides users familiar with generalized linear models with a
natural way of fitting parametric survival models. Moreover, their
framework is very flexible: general functions of time can be estimated
(e.g.~using splines or general additive models), and hence these models
retain some of the flexibility of Cox's partial likelihood approach. And
since the unit of analysis is a person moment, time-varying covariates
can also easily be included in this framework.

@@

\caption{\label{tab:bmtcrr-cis}Estimates and confidence intervals for the hazard ratios for each coefficient. Both estimates from case-base sampling and Cox regression are presented.}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Case-Base} & \multicolumn{2}{c}{Cox} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Covariates & HR & 95\% CI & HR & 95\% CI\\
\midrule
Sex & 0.74 & (0.43, 1.3) & 0.68 & (0.39, 1.19)\\
Disease & 0.52 & (0.29, 0.94) & 0.52 & (0.29, 0.93)\\
Phase (CR2 vs. CR1) & 1.20 & (0.48, 3) & 1.21 & (0.48, 3.02)\\
Phase (CR3 vs. CR1) & 1.59 & (0.41, 6.17) & 1.67 & (0.43, 6.5)\\
Phase (Relapse vs. CR1) & 4.09 & (1.9, 8.81) & 4.55 & (2.09, 9.9)\\
\addlinespace
Source & 1.70 & (0.55, 5.23) & 1.46 & (0.47, 4.54)\\
Age & 0.99 & (0.97, 1.02) & 0.99 & (0.97, 1.02)\\
\bottomrule
\end{tabular}
\end{table}

@@

Figure \ref{fig:compAbsrisk} shows the absolute risk curves for both
case-base sampling and the Fine-Gray model. As we can see, the two
approaches agree quite well for AML; however, there seems to be a
difference of about 5\% between the two curves for ALL. This difference
does not appear to be significant: the curve from case-base sampling is
contained within a 95\% confidence band around the Fine-Gray absolute
risk curve (figure not shown).

\hypertarget{case-study-3support-data}{%
\section{Case study 3---SUPPORT Data}\label{case-study-3support-data}}

@@

Next, we can use the object \code{cbFull} to estimate the absolute risk
curve on the test data. We first create a matrix \code{newx} containing
the relevant variables. Next, using \code{times}, we specify the time
points at which the cumulative incidence will be computed. Finally,
using the parameter \code{s = "lambda.1se"}, we specify at which value
of the tuning parameter we want to retrieve the coefficient estimates.

@@

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3FinalBrier} (A). There is separation between the
curves, but it is minimal. To better demonstrate the differences in
performance between the models, we compare Brier scores over time. In
Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our
penalized case-base model compared to both Cox regression models. The
differences, however, are minimal. All three outperform the Kaplan-Meier
estimator.

@@

\caption{\label{fig:cs3FinalBrier} Comparison of Cox regression, penalized Cox regression, penalized case-base estimation, and Kaplan-Meier. (A)  Probabilities of death as it changes over follow-up time. (B) Brier scores as they change over time, where a lower score corresponds to better performace. Penalized case-base estimation produced the lowest results over follow-up time.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

In the previous case studies, we only considered covariates that were
fixed at baseline. In this next case study, we will use the Stanford
Heart Transplant data
\citep[\citet{crowley1977covariance}]{clark1971cardiac} to show how
case-base sampling can also be used in the context of time-dependent
exposure. As an example that already appeared in the literature,
case-base sampling was used to study vaccination safety, where the
exposure period was defined as the week following vaccination
\citep{saarela2015case}. Hence, the main covariate of interest,
i.e.~exposure to the vaccine, was changing over time. In this context,
case-base sampling offers an efficient alternative to nested
case-control designs or self-matching.

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 
#>    827    791    790
\end{CodeOutput}
\end{CodeChunk}

As we can see, the best fit is the third model. By visualizing the
hazard functions for both exposed and unexposed individuals, we can more
clearly see how the hazards are no longer proportional. We can easily
obtain a plot of the hazards by using the \texttt{plot.singleEventCB}
method:

@@

\begin{CodeInput}
R> # Compute absolute risk curves
R> newdata <- data.frame(exposure = c(0, 1))
R> absrisk <- absoluteRisk(fit3,
R+   newdata = newdata,
R+   time = seq(0, 425, length.out = 100)
R+ )
R> 
R> class(absrisk)
\end{CodeInput}

@@

\begin{CodeInput}
R> 
R> plot(absrisk,
R+      id.names = c("No Tx", "Tx")) + 
R+   ylab("Cumulative Incidence") +
R+   xlab("Follow-up time (in days)") +
R+   paper_gg_theme
\end{CodeInput}

@@

As a methodological framework, case-base sampling is very flexible. Some
of this flexibility has been explored before in the literature: for
example, Saarela and Hanley \citeyearpar{saarela2015case} used case-base
sampling to model a time-dependent exposure variable in a vaccine safety
study. As another example, Saarela and Arjas
\citeyearpar{saarela2015non} combined case-base sampling and a Bayesian
non-parametric framework to compute individualized risk assessments for
chronic diseases. In the case studies above, we further explored this
flexibility along two fronts. On the one hand, we showed how splines
could be used as part of the linear predictor to model the effect of
time on the hazard. This strategy yielded estimates of the survival
function that were qualitatively similar to semiparametric estimates
derived from Cox regression; however, case-base sampling led to
estimates of the survival function that \emph{vary smoothly in time} and
are thus easier to interpret. On the other hand, we also displayed the
flexibility of case-base sampling by showing how it could be combined
with penalized logistic regression to perform variable selection.
Furthermore, the second and fourth case studies showed how case-base
sampling can respectively be applied to competing risks and time-varying
exposure settings. Even though we did not illustrate it in this article,
case-base sampling can also be combined with the framework of
\emph{generalized additive models}. This functionality has already been
implemented in the package. Similarly, case-base sampling can be
combined with quasi-likelihood estimation to fit survival models that
can account for the presence of over-dispersion. All of these examples
illustrate how the case-base sampling framework in general, and the
package \pkg{casebase} in particular, allows the user to fit a broad and
flexible family of survival functions.

@@

This report was generated on 2020-08-31 10:05:10 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.6
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.4             glue_1.4.1               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.2              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.1               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0.9000      
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_1.13.3    base64enc_0.1-3    
#>  [7] fs_1.4.1            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.0      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.55       tools_4.0.2         gtable_0.3.0       
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        iterators_1.0.12    xfun_0.15          
#> [37] rvest_0.3.6         lifecycle_0.2.0     polspline_1.1.17   
#> [40] muhaz_1.2.6.1       MASS_7.3-51.6       zoo_1.8-8          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.14        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_5.1-4           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.4        
#> [58] rlang_0.4.7         pkgconfig_2.0.3     evaluate_0.14      
#> [61] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [64] cmprsk_2.2-10       tidyselect_1.1.0    deSolve_1.28       
#> [67] plyr_1.8.6          R6_2.4.1            generics_0.0.2     
#> [70] Hmisc_4.4-0         multcomp_1.4-13     DBI_1.1.0          
#> [73] withr_2.2.0         pillar_1.4.6        haven_2.3.1        
#> [76] foreign_0.8-80      mgcv_1.8-31         nnet_7.3-14        
#> [79] mstate_0.2.12       modelr_0.1.8        crayon_1.3.4       
#> [82] rmarkdown_2.3       jpeg_0.1-8.1        grid_4.0.2         
#> [85] readxl_1.3.1        blob_1.2.1          reprex_0.3.0       
#> [88] digest_0.6.25       webshot_0.5.2       numDeriv_2016.8-1.1
#> [91] stats4_4.0.2        munsell_0.5.0       viridisLite_0.3.0  
#> [94] quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    editMax /Users/maxturgeon/Documents/git_repos/cbpaper
#> Head:     [0be28f4] 2020-08-25: switch to plot method for hazard
\end{CodeOutput}
\end{CodeChunk}
